### 2021-08-20 paper/paper.tex
update abstract and images

@@

\begin{figure}[h]
    \centering
    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_n.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_n.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of data points(Dimension: 64, Randomness: 1.0, Number of Classes: 10)}
    \label{Fig.1}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_d.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_d.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix(Number of Data Points: 100, Randomness: 1.0, Number of Classes: 10)}
    \label{Fig.2}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
    \caption{Loss value, parameter matrix error, accuracy versus randomness(Number of Data Points: 100, Dimension: 64, Number of classes: 10)}
    \label{Fig.3}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_class.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_class.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of classes(Number of Data Points: 100, Dimension: 64, Randomness: 1.0)}
    \label{Fig.4}

@@

\subsection{Pseudo-synthetic data}
In a pseudo-synthetic dataset, we take a non-synthetic dataset and modify it.
\fixme{describe your procedure for generating pseudo-synthetic data and all the experiments that you plan to run}
\subsubsection{Constructing Pseudo-synthetic datasets}
\label{sec:pseu-syn}
In order to compare the performance between classic cross entropy loss function and cover tree loss function, we need datasets which the classes have clear similarities.
Besides, we would like to construct pseudo-synthetic datasets which we can control the similarities.
The idea is we can generate the new classes from the original classes of datasets.
It means only the labels are synthetic and the features are real.
We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.

>>>>

\section{Abstract}
Softmax Cross Entropy loss function is widely used in neural network multi-class classification tasks. 
It treats every class equally while classes often have an inherent structure. We introduce cover tree loss function that build a cover tree structure between all classes by their similarities and provide the theoretical justification. 
We reparameterize the weight matrix by the cover tree structure of classes.
We compare cover tree loss with softmax cross entropy loss function on fully synthetic dataset and pseudo-synthetic dataset and real word dataset for multi-class classification tasks. 
The cover tree loss outperforms than softmax cross entropy loss function on metrics.

\section{Introduction}
When people do a standard multi-class classification task, the standard loss function is softmax cross entropy loss function.
The softmax cross entropy loss function

@@

\begin{figure}[h]
    \centering
    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_n.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_n.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}
    \label{Fig.1}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_d.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_d.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}
    \label{Fig.2}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
    \caption{Loss value, parameter matrix error, accuracy versus randomness($n=100, d=64, c=10$)}
    \label{Fig.3}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_class.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_class.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
    \label{Fig.4}

@@

\subsection{Pseudo-synthetic data}
In a pseudo-synthetic dataset, we take a non-synthetic dataset and modify it.
\fixme{describe your procedure for generating pseudo-synthetic data and all the experiments that you plan to run}
\subsubsection{Constructing Pseudo-synthetic datasets}
\label{sec:pseu-syn}
In order to compare the performance between classic cross entropy loss function and cover tree loss function, we need datasets which the classes have clear similarities.
Besides, we would like to construct pseudo-synthetic datasets which we can control the similarities.
The idea is we can generate the new classes from the original classes of datasets.
This impilies only the labels are synthetic and the features are real.
We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.
